From Big Data to Big Displays\\ High-Performance Visualization at Blue Brain

### 2017-06-02 paper.tex
Update Authors

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{Stefan~Eilemann, et.al.\thanks{\textit{firstname.lastname}@epfl.ch}}
\institute{Blue Brain Project, Ecole Polytechnique Federale de Lausanne}

@@

Tide (Tiled Interactive Display Environment) is the software driving the Blue
Brain tiled display walls and OpenDeck. It provides multi-window, multi-user
touch interaction on large surfaces --- think of a giant collaborative
wall-mounted tablet. Tide is a distributed application that can run on multiple
machines to power display walls or projection systems of any size. Its user
interface is designed to offer an intuitive experience on touch walls. It works
just as well on non touch-capable installations by using its web interface from
any web browser. \fig{fTDW} shows Tide on a $4\times 3$ display wall and
\fig{fTideWeb} shows the Tide web interface in a browser.

>>>>

%% Author and Affiliation (multiple authors with multiple affiliations)
\author{\small Stefan~Eilemann, Marwan~Abdellah, Nicolas~Antille, Ahmet~Bilgili, Grigory~Chevtchenko, Raphael~Dumusc, Cyrille~Favreau, Juan~Hernando, Daniel~Nachbaur, Pawel~Podhajski, Jafet~Villafranca\thanks{\textit{firstname.lastname}@epfl.ch}}
\institute{Blue Brain Project, Ecole Polytechnique Federale de Lausanne}

@@

Tide (Tiled Interactive Display Environment) is the software driving the Blue
Brain tiled display walls and the future OpenDeck. It provides multi-window,
multi-user touch interaction on large surfaces --- think of a giant
collaborative wall-mounted tablet. Tide is a distributed application that can
run on multiple machines to power display walls or projection systems of any
size. Its user interface is designed to offer an intuitive experience on touch
walls. It works just as well on non touch-capable installations by using its web
interface from any web browser. \fig{fTDW} shows Tide on a $4\times 3$ display
wall and \fig{fTideWeb} shows the Tide web interface in a browser.
